Dependent Object Types

### 2012-08-06 article.tex
some cases of proof

% Logical relations
\newcommand{\relv}[4]{\mathcal{V}_{#1;#2;#3}\llbracket#4\rrbracket}
\newcommand{\rele}[4]{\mathcal{E}_{#1;#2;#3}\llbracket#4\rrbracket}
\newcommand{\rels}[3]{\mathcal{S}_{#1;#2}\llbracket#3\rrbracket}
\newcommand{\relg}[3]{\mathcal{G}_{#1;#2}\llbracket#3\rrbracket}
\newcommand{\irred}[2]{\text{irred }(#1,#2)}
\newcommand{\andl}{\;\wedge}
\newcommand{\orl}{\vee}
\newcommand{\impliesl}{\rightarrow}
\newcommand{\reductionl}[5]{#1 \operatorname{|} #2 \;\rightarrow^{#5}\; #3 \operatorname{|} #4}
\newcommand{\ds}{\,\vDash\,}

@@

>>>>

% Logical relations
\newcommand{\relv}[4]{\mathcal{V}_{#1;#2;#3}\llbracket#4\rrbracket}
\newcommand{\rele}[4]{\mathcal{E}_{#1;#2;#3}\llbracket#4\rrbracket}
\newcommand{\rels}[3]{\mathcal{S}_{#1;#2}\llbracket#3\rrbracket}
\newcommand{\relg}[3]{\mathcal{G}_{#1;#2}\llbracket#3\rrbracket}
\newcommand{\irred}[2]{\text{irred }(#1,#2)}
\newcommand{\andl}{\;\wedge\;}
\newcommand{\orl}{\vee}
\newcommand{\impliesl}{\rightarrow}
\newcommand{\reductionl}[5]{#1 \operatorname{|} #2 \;\rightarrow^{#5}\; #3 \operatorname{|} #4}
\newcommand{\ds}{\,\vDash\,}

@@

\begin{myproof}
The proof is on induction on the derivation of $\Gamma \ts t : T$.

\Case \textsc{var}: $\Gamma \ts x : T$ knowing $(x : T) \in
\Gamma$.

Need to show $x \in \rele k \Gamma - T$. Suppose $k > 0$ and $s \in
\rels k \Gamma -$. Remains to show $x \in \relv {k-1} \Gamma s
T$. This follows from the definition of $\mathcal{G}$.

\Case \textsc{sel}: $\Gamma \ts t_1.l_i : T$ knowing $\Gamma \ts t_1 :
T_1$, $\Gamma \ts T_1 \expand_z \seq{D}$, $l_i : V_i \in \seq{D}$ and
knowing either that $t_1 = p_1 \andl T = \subst p z {V_i}$ or that $z
\not\in \fn(V_i) \andl T = V_i$.

Need to show $t_1.l_i \in \rele k \Gamma - T$. Suppose $k > 0$ and $s
\in \rels k \Gamma -$. Suppose $\reductionl {t_1.l_i} s {t'} {s'}
\andl \irred {t'} {s'} \andl \Gamma' \in \relg \Gamma k {s'}
\Gamma$. Remains to show ${t'} \in \relv {k-j-1} {\Gamma'} {s'} T$.

By operational semantics, $\reductionl {t_1} s {t_1'} {s'} {j-1}$ and
$\irred {t_1'} {s'}$. By induction hypothesis, ${t_1'} \in \relv
{k-j+1-1} {\Gamma'} {s'} {T_1}$.

By operational semantics, $\reductionl {t_1'.l_i} {s'} {t'} {s'}
1$. Since ${t_1'} \in \relv {k-j} {\Gamma'} {s'} {T_1}$, we can
conclude $t' \in \relv {k-j-1} {\Gamma'} {s'} T$ from the clause for
value labels.

\Case \textsc{msel}: \todo{case}.

\Case \textsc{new}: \todo{case}.

\end{myproof}
